---
title: "Survival analysis in patients with HCC treated with TACE Subset Group(n=20)"
author: "Sultan Alharbi"
date: "`r Sys.Date()`"
output:
  UHHformats::html_material:
    highlight: kate
    code_folding: show
    card: true
  html_document:
    df_print: paged
    fig_caption: true
    fig_height: 8
    fig_width: 10
    keep_md: true
bibliography:
- /Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/Sultan Thesis R scripts/bib/references.bib
csl: "/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/bib/sage-harvard.csl"
logo: /Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/MyLogo.jpg
editor_options:
  chunk_output_type: inline
---


```{r setup, include=FALSE}
# Load necessary libraries here, e.g., library(tidyverse)

knitr::opts_chunk$set(
  # Code display options
  echo = TRUE,        # Display code chunks in the output
  
  # Caching options for speed
  cache = TRUE,       # Cache chunk results to avoid re-running code
  
  # Suppress messages for a cleaner report
  warning = FALSE,    # Don't show warnings in the final report
  message = FALSE,    # Don't show messages in the final report
  
  # Figure options
  fig.align = 'center', # Center-align all figures
  fig.width = 10,       # Figure width in inches
  fig.height = 8,       # Figure height in inches
  dpi = 300,            # Figure resolution in DPI (dots per inch)
  fig.retina = 2,       # Improve figure resolution for high-res (Retina) screens
  dev = 'png',          # Graphics device (png, svg, pdf, etc.)
  
  # Output size option for better layout control
  out.width = "80%"     # Set output width to 80% of the container
)

# also set theme options for plotting libraries like ggplot2
# For example:
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 14))
```


# [) ✍️ Introduction to HCC and TACE-based treatment]{style="color:#000000; font-weight:bold;"} {.tabset .tabset-fade .tabset-pills}

## [Project Overview]{style="color:#765543; font-weight:bold;"}

::::: {.section-box .primary-box}
::: {style="font-weight:bold; color:#1A4F8B; margin-bottom:5px;"}
Research Context ![HCC_TACE](/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/Images/Liver_image.png){width="200px"}
:::

<div>

This script analyzes targeted sequencing data from patients with hepatocellular carcinoma (HCC) who have been treated with transarterial chemoembolization (TACE) as part of my PhD thesis research project.

</div>
:::::

## [Analysis Methods]{style="color:#765543; font-weight:bold;"}

::::: {.section-box .secondary-box}
::: {style="font-weight:bold; color:#2E7D32; margin-bottom:5px;"}
Statistical Approach
:::

<div>

The analysis utilizes Kaplan-Meier survival curves and Cox proportional hazards models to evaluate overall survival (OS) and progression-free survival (PFS) in HCC patients treated with TACE.

</div>
:::::


# [) ⚙️ Data Preparation and Loading Packages]{style="color:#000000; font-weight:bold;"} {.tabset .tabset-fade}

## [Load and Inspect Data]{style="color:#765543; font-weight:bold;"}

```{r Load_Data, echo=TRUE, cache=TRUE}
# Load the data
Survival_R <- read.csv("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Tables/Final_PFS_OS_TACE.csv")

# Create binary variables
# cfDNA binary variable
Survival_R$cfDNA <- ifelse(Survival_R$`cfDNA1.Result.ng.ml..pre.TACE.` < 544, 0, 1)

# Tumour Size binary variable (< 5 vs >= 5 cm)
Survival_R$Tumour_size <- ifelse(Survival_R$Tumour_size < 5, 0, 1)

# AFP binary variable (< 400 vs >= 400)
Survival_R$AFP_binary <- ifelse(Survival_R$AFP < 400, 0, 1)

# Albumin binary variable (< 36 vs >= 36)
Survival_R$Albumin_binary <- ifelse(Survival_R$Albumin < 36, 0, 1)

# Bilirubin binary variable (< 11 vs >= 11)
Survival_R$Bilirubin_binary <- ifelse(Survival_R$Bilirubin < 11, 0, 1)

# Age binary variable (< 69 vs >= 69)
Survival_R$Age_binary <- ifelse(Survival_R$Age < 69, 0, 1)

# Print the summary of the data
summary(Survival_R)
```

## [Install Necessary Packages]{style="color:#765543; font-weight:bold;"}

```{r load-packages, include = TRUE, echo = TRUE, cache=TRUE}
# Function to safely install and load packages
install_and_load <- function(packages, bioconductor = FALSE) {
  # Set a default CRAN mirror if not already set
  if (is.null(getOption("repos"))) {
    options(repos = "https://cran.r-project.org")
  }
  
  for (package in packages) {
    # Check if package is installed
    if (!requireNamespace(package, quietly = TRUE)) {
      message(paste("Installing package:", package))
      
      # Install from appropriate source
      if (bioconductor) {
        if (!requireNamespace("BiocManager", quietly = TRUE)) {
          install.packages("BiocManager")
        }
        BiocManager::install(package, update = FALSE, ask = FALSE)
      } else {
        install.packages(package)
      }
    }
    
    # Load package
    suppressWarnings(suppressPackageStartupMessages(
      library(package, character.only = TRUE)
    ))
  }
}

# Install and load remotes package first
install_and_load("remotes")

# Install maftools from GitHub if needed
if (!"maftools" %in% installed.packages()[,"Package"]) {
  remotes::install_github("PoisonAlien/maftools", quiet = TRUE)
}

# Regular CRAN packages
cran_packages <- c("survival", "lubridate", "ggfortify", "flexsurv", "remotes", 
                   "evaluate", "knitr", "dplyr", "ggplot2", "magrittr", "grid",
                   "broom.helpers", "modelsummary", "kableExtra", "tinytex", "ggplotify")

# Bioconductor packages
bioc_packages <- c("ggsurvfit", "gtsummary", "tidycmprsk", "ranger", 
                   "survminer", "survcomp", "maftools")

# Install and load packages
install_and_load(cran_packages)
install_and_load(bioc_packages, bioconductor = TRUE)

# Install tinytex package and TinyTeX if not already installed
if (!requireNamespace("tinytex", quietly = TRUE)) {
  install.packages("tinytex")
}
if (!tinytex::is_tinytex()) {
  tinytex::install_tinytex()
}

# Create bibliography directory if it doesn't exist
if (!dir.exists("bib")) {
  dir.create("bib")
}

# Install UHHformats if needed
if (!requireNamespace("UHHformats", quietly = TRUE)) {
  # First try CRAN
  tryCatch({
    install.packages("UHHformats")
  }, error = function(e) {
    # If CRAN fails, try R-forge
    install.packages("UHHformats", repos = "https://uhh-r.r-forge.r-project.org")
  })
}

# Generate package references
all_packages <- c(.packages(), 'rmarkdown', 'UHHformats', 'knitr')
knitr::write_bib(x = all_packages, file = 'bib/packages.bib')
```

## [Helper Functions]{style="color:#765543; font-weight:bold;"}

```{r Helper_Functions, echo=TRUE, cache=TRUE}
############################################################
# Function to create survival plots with annotations for whole cohort
############################################################
create_whole_cohort_survival_plot <- function(surv_fit, title, time_col, status_col, ylab, annotation_x, annotation_y) {
  # Get median survival and CI
  median_surv <- surv_median(surv_fit)
  
  # Create the survival plot
  surv_plot <- ggsurvplot(surv_fit,
                         conf.int = TRUE,
                         pval = FALSE,
                         pval.method = FALSE,
                         risk.table = TRUE,
                         surv.median.line = "hv",
                         legend.title = title,
                         xlab = "Time, months",
                         ylab = ylab,
                         palette = "blue")  # Single color for whole cohort
  
  # Create label text
  label_text <- sprintf("Median %s: %.2f months\n95%% CI: %.2f - %s", 
                       ylab, median_surv$median[1], median_surv$lower[1], 
                       if(is.na(median_surv$upper[1])) "NA" else sprintf("%.2f", median_surv$upper[1]))
  
  # Add annotation
  surv_plot$plot <- surv_plot$plot +
    annotate("label", x = annotation_x, y = annotation_y, label = label_text,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "lightblue")
  
  return(surv_plot)
}

############################################################
# Function to create survival plots for three groups (A, B, C)
############################################################
create_survival_plot <- function(surv_fit, title, column_name, median_surv, time_col, status_col, ylab, annotation_x, annotation_y1, annotation_y2, annotation_y3, pval_y) {
  # Perform the log-rank test to get the p-value
  formula <- as.formula(paste("Surv(", time_col, ",", status_col, ") ~", column_name))
  logrank_test <- survdiff(formula, data = Survival_R)
  p_value <- 1 - pchisq(logrank_test$chisq, df = length(unique(Survival_R[[column_name]])) - 1)
  
  # Create the survival plot
  surv_plot <- ggsurvplot(surv_fit,
                          conf.int = FALSE,
                          pval = FALSE,
                          pval.method = FALSE,
                          risk.table = TRUE,
                          surv.median.line = "hv",
                          legend.labs = c("A", "B", "C"),
                          legend.title = title,
                          xlab = "Time, months",
                          ylab = ylab,
                          palette = c("#00BA38", "#619CFF", "#F8766D"))  # Set green, blue, red for A, B, C
  
  # Create label texts
  label_A <- sprintf("Class A \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[1], median_surv$lower[1], 
                    if(is.na(median_surv$upper[1])) "NA" else sprintf("%.2f", median_surv$upper[1]))
  
  label_B <- sprintf("Class B \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[2], median_surv$lower[2], 
                    if(is.na(median_surv$upper[2])) "NA" else sprintf("%.2f", median_surv$upper[2]))
  
  label_C <- sprintf("Class C \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[3], median_surv$lower[3], 
                    if(is.na(median_surv$upper[3])) "NA" else sprintf("%.2f", median_surv$upper[3]))
  
  # Add annotations with matching colors
  surv_plot$plot <- surv_plot$plot +
    annotate("label", x = annotation_x, y = annotation_y1, label = label_A,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#00BA38") +  # Green for Class A
    annotate("label", x = annotation_x, y = annotation_y2, label = label_B,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#619CFF") +  # Blue for Class B
    annotate("label", x = annotation_x, y = annotation_y3, label = label_C,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#F8766D") +  # Red for Class C
    annotate("text", x = annotation_x, y = pval_y, 
             label = sprintf("Log-rank p-value: %.4f", p_value),
             size = 4, hjust = 0, vjust = 1, color = "black")
  
  return(surv_plot)
}

############################################################
# Function to create survival plots for two groups (A, B)
############################################################
create_survival_plot_two_groups <- function(surv_fit, title, column_name, median_surv, time_col, status_col, ylab, annotation_x, annotation_y1, annotation_y2, pval_y) {
  # Perform the log-rank test to get the p-value
  formula <- as.formula(paste("Surv(", time_col, ",", status_col, ") ~", column_name))
  logrank_test <- survdiff(formula, data = Survival_R)
  p_value <- 1 - pchisq(logrank_test$chisq, df = 1)
  
  # Create the survival plot
  surv_plot <- ggsurvplot(surv_fit,
                          conf.int = FALSE,
                          pval = FALSE,
                          pval.method = FALSE,
                          risk.table = TRUE,
                          surv.median.line = "hv",
                          legend.labs = c("A", "B"),
                          legend.title = title,
                          xlab = "Time, months",
                          ylab = ylab,
                          palette = c("#00BA38", "#619CFF"))  # Set green, blue for A, B
  
  # Create label texts
  label_A <- sprintf("Class A \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[1], median_surv$lower[1], 
                    if(is.na(median_surv$upper[1])) "NA" else sprintf("%.2f", median_surv$upper[1]))
  
  label_B <- sprintf("Class B \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[2], median_surv$lower[2], 
                    if(is.na(median_surv$upper[2])) "NA" else sprintf("%.2f", median_surv$upper[2]))
  
  # Add annotations with matching colors
  surv_plot$plot <- surv_plot$plot +
    annotate("label", x = annotation_x, y = annotation_y1, label = label_A,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#00BA38") +  # Green for Class A
    annotate("label", x = annotation_x, y = annotation_y2, label = label_B,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#619CFF") +  # Blue for Class B
    annotate("text", x = annotation_x, y = pval_y, 
             label = sprintf("Log-rank p-value: %.4f", p_value),
             size = 4, hjust = 0, vjust = 1, color = "black")
  
  return(surv_plot)
}

############################################################
# Function to create survival plots for binary variables (0/1)
############################################################
create_survival_plot_binary <- function(surv_fit, title, column_name, median_surv, time_col, status_col, ylab, annotation_x, annotation_y1, annotation_y2, pval_y, label0, label1) {
  # Perform the log-rank test to get the p-value
  formula <- as.formula(paste("Surv(", time_col, ",", status_col, ") ~", column_name))
  logrank_test <- survdiff(formula, data = Survival_R)
  p_value <- 1 - pchisq(logrank_test$chisq, df = 1)
  
  # Create the survival plot
  surv_plot <- ggsurvplot(surv_fit,
                          conf.int = FALSE,
                          pval = FALSE,
                          pval.method = FALSE,
                          risk.table = TRUE,
                          surv.median.line = "hv",
                          legend.labs = c(label0, label1),  # Use custom labels instead of 0, 1
                          legend.title = title,
                          xlab = "Time, months",
                          ylab = ylab,
                          palette = c("#00BA38", "#619CFF"))  # Set green, blue for 0, 1
  
  # Create label texts
  label_0 <- sprintf("%s \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    label0, ylab, median_surv$median[1], median_surv$lower[1], 
                    if(is.na(median_surv$upper[1])) "NA" else sprintf("%.2f", median_surv$upper[1]))
  
  label_1 <- sprintf("%s \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    label1, ylab, median_surv$median[2], median_surv$lower[2], 
                    if(is.na(median_surv$upper[2])) "NA" else sprintf("%.2f", median_surv$upper[2]))
  
  # Add annotations with matching colors
  surv_plot$plot <- surv_plot$plot +
    annotate("label", x = annotation_x, y = annotation_y1, label = label_0,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#00BA38") +  # Green for value 0
    annotate("label", x = annotation_x, y = annotation_y2, label = label_1,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#619CFF") +  # Blue for value 1
    annotate("text", x = annotation_x, y = pval_y, 
             label = sprintf("Log-rank p-value: %.4f", p_value),
             size = 4, hjust = 0, vjust = 1, color = "black")
  
  return(surv_plot)
}

############################################################
# Function to create survival plots for HAP (A, B, C, D)
############################################################
create_survival_plot_HAP <- function(surv_fit, title, column_name, median_surv, time_col, status_col, ylab, annotation_x, annotation_y1, annotation_y2, annotation_y3, annotation_y4, pval_y) {
  # Perform the log-rank test to get the p-value
  formula <- as.formula(paste("Surv(", time_col, ",", status_col, ") ~", column_name))
  logrank_test <- survdiff(formula, data = Survival_R)
  p_value <- 1 - pchisq(logrank_test$chisq, df = length(levels(factor(Survival_R[[column_name]]))) - 1)
  
  # Create the survival plot
  surv_plot <- ggsurvplot(surv_fit,
                          conf.int = FALSE,
                          pval = FALSE,
                          pval.method = FALSE,
                          risk.table = TRUE,
                          surv.median.line = "hv",
                          legend.labs = c("A", "B", "C", "D"),  # Use A, B, C, D for HAP
                          legend.title = title,
                          xlab = "Time, months",
                          ylab = ylab,
                          palette = c("#00BA38", "#619CFF", "#F8766D", "#9467BD"))  # Green, Blue, Red, Purple
  
  # Create label texts
  label_A <- sprintf("HAP A \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[1], median_surv$lower[1], 
                    if(is.na(median_surv$upper[1])) "NA" else sprintf("%.2f", median_surv$upper[1]))
  
  label_B <- sprintf("HAP B \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[2], median_surv$lower[2], 
                    if(is.na(median_surv$upper[2])) "NA" else sprintf("%.2f", median_surv$upper[2]))
  
  label_C <- sprintf("HAP C \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[3], median_surv$lower[3], 
                    if(is.na(median_surv$upper[3])) "NA" else sprintf("%.2f", median_surv$upper[3]))
  
  label_D <- sprintf("HAP D \nMedian %s: %.2f months\n95%% CI: %.2f - %s", 
                    ylab, median_surv$median[4], median_surv$lower[4], 
                    if(is.na(median_surv$upper[4])) "NA" else sprintf("%.2f", median_surv$upper[4]))
  
  # Add annotations with matching colors
  surv_plot$plot <- surv_plot$plot +
    annotate("label", x = annotation_x, y = annotation_y1, label = label_A,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#00BA38") +  # Green for HAP A
    annotate("label", x = annotation_x, y = annotation_y2, label = label_B,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#619CFF") +  # Blue for HAP B
    annotate("label", x = annotation_x, y = annotation_y3, label = label_C,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#F8766D") +  # Red for HAP C
    annotate("label", x = annotation_x, y = annotation_y4, label = label_D,
             size = 4, hjust = 0, vjust = 1, color = "black", fill = "#9467BD") +  # Purple for HAP D
    annotate("text", x = annotation_x, y = pval_y, 
             label = sprintf("Log-rank p-value: %.4f", p_value),
             size = 4, hjust = 0, vjust = 2, color = "black")
  
  return(surv_plot)
}
```

# [) 📉 Kaplan-Meier Survival Analysis]{style="color:#000000; font-weight:bold;"} {.tabset .tabset-fade .tabset-pills}

## [Whole Cohort Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival (OS)]{style="color:#51366a; font-weight:bold;"}

```{r OS_Whole_Cohort, echo=TRUE, cache=TRUE}
# OS Analysis for Whole Cohort
Whole_Cohort_OS <- survfit(Surv(OS_Time, OS_Status) ~ 1, data = Survival_R)
Whole_OS_plot <- create_whole_cohort_survival_plot(Whole_Cohort_OS, "Strata", 
                                                  "OS_Time", "OS_Status", 
                                                  "OS Probability", 80, 0.75)

# Display plot
print(Whole_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Whole_Cohort_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Whole_OS_plot)
dev.off()
```

::::: {.section-box .primary-box}
::: {style="font-weight:bold; color:#1A4F8B; margin-bottom:5px;"}
Results interpretation ![HCC_TACE](/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/Images/resultsLogo.jpg){width="200px"}
:::

<div>

**Confident Interval (CI)**: The median OS for the whole cohort is ***34.30 months (~ 3 years)*** with a 95% CI of 27.80 to 41.30 months, indicating a range where I can be 95% confident 🧐 that the true median OS for this HCC cohorts lies somewhere between approximately 28 to 41 months.

</div>
:::::

### [Progression-Free Survival (PFS)]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Whole_Cohort, echo=TRUE, cache=TRUE}
# PFS Analysis for Whole Cohort
Whole_Cohort_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ 1, data = Survival_R)
Whole_PFS_plot <- create_whole_cohort_survival_plot(Whole_Cohort_PFS, "Strata", 
                                                   "PFS_Time", "PFS_Status", 
                                                   "PFS Probability", 40, 0.75)

# Display plot
print(Whole_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Whole_Cohort_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Whole_PFS_plot)
dev.off()
```

::::: {.section-box .primary-box}

::: {style="text-align: center; margin-bottom:10px;"}
![](/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/Images/178.jpg){width="300px"}
:::

::: {style="font-weight:bold; color:red; margin-bottom:5px;"}
How effective is TACE for treating HCC patients?
:::

::: {style="font-weight:bold; color:green; margin-bottom:5px;"}
This plot shows me how long HCC patients live without their cancer getting worse after TACE treatment.
PFS measures the time from the start of treatment 💊 🕛 until one of the following events occurs:

A) The cancer shows signs of progression (e.g., tumors grow in size or new tumors appear 👹).
B) The patient dies from any cause 😔.

This plot tracks the PFS for a cohort of 103 patients over a 60-month (5-year) period.
:::

**Results Interpretation**

The median Progression-Free Survival (PFS) for the entire patient cohort was **12.43 months** (approximately more than 1 years), with a 95% confidence interval (CI) of 10.03 to 18.47 months. This indicates a 95% probability that the true median PFS for this cohort of HCC patients lies between approximately 10 and 18 months.

<span style="color:#6638f0; font-weight:bold;">The central finding here:</span> is the median PFS of **12.43 months**. This means that after TACE treatment, half of the patients lived for approximately <span style="color:#049840; font-weight:bold;">**one year**</span> 🥳 before their disease progressed. The dashed lines clearly illustrate how this point is determined, linking the 50% probability mark to the corresponding time.

**Confidence Interval (CI) Explained:**

The 95% CI provides a range of plausible values for the median PFS. In this case, we can be 95% confident that the actual median PFS for the population from which this sample was drawn falls between 10 and 18 months. The width of this interval also gives an indication of the precision of the estimate; a narrower interval would suggest a more precise estimate.
:::::


## [BCLC Stage Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by BCLC Stage]{style="color:#51366a; font-weight:bold;"}

```{r OS_BCLC, echo=TRUE, cache=TRUE}
# OS Analysis by BCLC Stage
BCLC_OS <- survfit(Surv(OS_Time, OS_Status) ~ BCLC, data = Survival_R)
median_os <- surv_median(BCLC_OS)

BCLC_OS_plot <- create_survival_plot(BCLC_OS, "BCLC", "BCLC", median_os, "OS_Time", "OS_Status", 
                                    "OS Probability", 80, 0.95, 0.75, 0.55, 0.35)

# Display plot
print(BCLC_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/BCLC_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(BCLC_OS_plot)
dev.off()
```

::::: {.section-box .primary-box}

<div style="display: flex; justify-content: center; gap: 20px; margin-bottom:10px;">
<div style="text-align: center;">
<img src="/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/Images/BCLC2.png" width="400px" height="400px" alt="BCLC Stage 2">
<p><em>Figure 1</em></p>
</div>
<div style="text-align: center;">
<img src="/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/Images/BCLC1.png" width="400px" height="400px" alt="BCLC Stage 1">
<p><em>Figure 2</em></p>
</div>
</div>

::: {style="font-weight:bold; color:red; margin-bottom:5px;"}
How can BCLC effect TACE efficacy?
:::

::: {style="font-weight:bold; color:green; margin-bottom:5px;"}
BCLC is a standard system that classifies HCC based on:

1️⃣ Tumor characteristics.

2️⃣ Liver function.

3️⃣ Patient health.

with Class A being early-stage, B being intermediate, and C being advanced-stage of HCC.
:::

**Results Interpretation**

**Overall Survival (OS) by BCLC Class**
This plot shows the probability of patients being alive over a 10-year period, grouped by their cancer stage at the start of the study.

<span style="color:#5cc9f5; font-weight:bold;">**Key Findings:**</span> 🥳


<span style="color:#028236; font-weight:bold;">**Class A:**</span> This early-stage group has the best prognosis. The median OS is 60.73 months (about 5 years). The confidence interval is "NA" (Not Available/Not Applicable) on the upper end because fewer than 50% of the patients in this group had died by the end of the follow-up period, which is a very positive sign ✅.


<span style="color:#0843A9; font-weight:bold;">**Class  B:**</span>& <span style="color:#A90813; font-weight:bold;">**Class  C:**</span> These intermediate (B) and advanced-stage (C) groups have much shorter survival. Their median OS is 30.80 months and 33.27 months, respectively.

**The Log-Rank p-value:** This is a crucial piece of information. The p-value of 0.2425 tests the hypothesis that there is no difference in survival among the three groups. Since this value is much greater than the standard significance threshold of 0.05, it means that the observed differences in Overall Survival between Classes A, B, and C are **NOT** statistically significant 🥴.

**Clinical Interpretation:**
While Class A patients visually appear to do better, the statistical test tells us we cannot confidently conclude that BCLC stage was a predictor of overall lifespan in this specific patient cohort. The crossing curves of Class B and C and the lack of statistical significance suggest that other factors—most likely the type and success of treatments received after the initial TACE—played a major role in determining a patient's final survival time.

:::::




### [Progression-Free Survival by BCLC Stage]{style="color:#51366a; font-weight:bold;"}

```{r PFS_BCLC, echo=TRUE, cache=TRUE}
# PFS Analysis by BCLC Stage
BCLC_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ BCLC, data = Survival_R)
median_pfs <- surv_median(BCLC_PFS)

BCLC_PFS_plot <- create_survival_plot(BCLC_PFS, "BCLC", "BCLC", median_pfs, "PFS_Time", "PFS_Status", 
                                     "PFS Probability", 40, 0.97, 0.77, 0.57, 0.40)

# Display plot
print(BCLC_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/BCLC_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(BCLC_PFS_plot)
dev.off()
```


::::: {.section-box .primary-box}

<div style="display: flex; justify-content: center; gap: 20px; margin-bottom:10px;">
<div style="text-align: center;">
<img src="/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Scripts/Images/SuperMan_TACE.png" width="400px" height="400px" alt="BCLC Stage 2">
<p><em>Figure 1</em></p>
</div>
</div>

::: {style="font-weight:bold; color:red; margin-bottom:5px;"}
How can different BCLC stages effect TACE efficacy?
:::

::: {style="font-weight:bold; color:green; margin-bottom:5px;"}
This plot shows the probability of patients being alive and their cancer not having progressed 💪, grouped by their initial BCLC stage. This is a measure of how long the initial treatment (like TACE) remains effective.
:::
<span style="color:#5cc9f5; font-weight:bold;">**Key Findings:**</span> 🥳

::: {style="font-weight:bold; color:black; margin-bottom:5px;"}
Clear Separation of Curves: Unlike the OS plot, these curves are cleanly separated in the clinically expected order.
<span style="color:#028236; font-weight:bold;">**Class A:**</span> Has the longest period of disease control, with a median PFS of 21.30 months 🥇.
<span style="color:#0843A9; font-weight:bold;">**Class  B:**</span> Has an intermediate median PFS of 11.53 months 🥈.
<span style="color:#A90813; font-weight:bold;">**Class  C:**</span> Has the shortest period of disease control, with a median PFS of only 5.83 months 🥉.


**The Log-Rank p-value:** Here, the p-value is ***0.0128***. Since this value is less than 0.05, it means there is a statistically significant difference in Progression-Free Survival among the three BCLC classes.

The PFS data clearly and significantly (p=0.0128) demonstrates that BCLC staging is a **prognostic indicator 🔍** for tumour (HCC) control following TACE.
:::



<span style="color:#0516D3; font-weight:bold;">**Clinical Interpretation:**</span> 👩🏻‍⚕️

This result is very clear: BCLC stage is an excellent predictor of how long a patient's cancer will remain stable after initial therapy. Patients with earlier-stage disease derive a much longer benefit from treatment before their cancer begins to grow again.

<span style="color:#909703; font-weight:bold;">**The Complete Story Comparing the two plots tells a powerful story:**</span> 🚶

PFS shows the effect of initial treatment: The PFS plot clearly and significantly shows that the initial BCLC stage dictates how long a therapy like TACE can control the cancer. Earlier stage (A) means longer control; advanced stage (C) means shorter control.
OS shows the effect of all subsequent treatments: The OS plot is "messier" and not statistically significant. This strongly suggests that what happens after a patient's cancer first progresses is critical to their ultimate survival. A patient in Class C might progress quickly (short PFS) but then receive an effective second-line therapy (like immunotherapy or TKI) that extends their life significantly, allowing them to live as long as, or even longer than, some patients who started in Class B.
In conclusion, BCLC stage is a robust tool for predicting the duration of disease control (PFS), but its ability to predict overall lifespan (OS) can be blurred by the complex, multi-step treatment journey of modern cancer care.
:::::









## [CTP Class Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by CTP Class]{style="color:#51366a; font-weight:bold;"}

```{r OS_CTP, echo=TRUE, cache=TRUE}
# OS Analysis by CTP class
CTP_OS <- survfit(Surv(OS_Time, OS_Status) ~ CTP, data = Survival_R)
median_os <- surv_median(CTP_OS)

CTP_OS_plot <- create_survival_plot_two_groups(CTP_OS, "CTP", "CTP", median_os, "OS_Time", "OS_Status", 
                                   "OS Probability", 80, 0.95, 0.75, 0.55)

# Display plot
print(CTP_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/CTP_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(CTP_OS_plot)
dev.off()
```

### [Progression-Free Survival by CTP Class]{style="color:#51366a; font-weight:bold;"}

```{r PFS_CTP, echo=TRUE, cache=TRUE}
# PFS Analysis by CTP class
CTP_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ CTP, data = Survival_R)
median_pfs <- surv_median(CTP_PFS)

CTP_PFS_plot <- create_survival_plot_two_groups(CTP_PFS, "CTP", "CTP", median_pfs, "PFS_Time", "PFS_Status", 
                                    "PFS Probability", 40, 0.97, 0.77, 0.57)

# Display plot
print(CTP_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/CTP_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(CTP_PFS_plot)
dev.off()
```

## [ECOG-PS Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by PS]{style="color:#51366a; font-weight:bold;"}

```{r OS_PS, echo=TRUE, cache=TRUE}
# OS Analysis by PS
PS_OS <- survfit(Surv(OS_Time, OS_Status) ~ PS, data = Survival_R)
median_os <- surv_median(PS_OS)

PS_OS_plot <- create_survival_plot_binary(PS_OS, "Performance Status", "PS", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "PS 0", "PS 1")

# Display plot
print(PS_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/PS_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(PS_OS_plot)
dev.off()
```

### [Progression-Free Survival by PS]{style="color:#51366a; font-weight:bold;"}

```{r PFS_PS, echo=TRUE, cache=TRUE}
# PFS Analysis by PS
PS_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ PS, data = Survival_R)
median_pfs <- surv_median(PS_PFS)

PS_PFS_plot <- create_survival_plot_binary(PS_PFS, "Performance Status", "PS", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "PS 0", "PS 1")

# Display plot
print(PS_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/PS_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(PS_PFS_plot)
dev.off()
```

## [HAP Class Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by HAP Class]{style="color:#51366a; font-weight:bold;"}

```{r OS_HAP, echo=TRUE, cache=TRUE}
# OS Analysis by HAP
HAP_OS <- survfit(Surv(OS_Time, OS_Status) ~ HAP, data = Survival_R)
median_os <- surv_median(HAP_OS)

HAP_OS_plot <- create_survival_plot_HAP(HAP_OS, "HAP", "HAP", median_os, "OS_Time", "OS_Status", 
                                   "OS Probability", 80, 1, 0.83, 0.66, 0.49, 0.35)

# Display plot
print(HAP_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/HAP_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(HAP_OS_plot)
dev.off()
```

### [Progression-Free Survival by HAP Class]{style="color:#51366a; font-weight:bold;"}

```{r PFS_HAP, echo=TRUE, cache=TRUE}
# PFS Analysis by HAP
HAP_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ HAP, data = Survival_R)
median_pfs <- surv_median(HAP_PFS)

HAP_PFS_plot <- create_survival_plot_HAP(HAP_PFS, "HAP", "HAP", median_pfs, "PFS_Time", "PFS_Status", 
                                    "PFS Probability", 40, 1, 0.83, 0.66, 0.49, 0.35)

# Display plot
print(HAP_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/HAP_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(HAP_PFS_plot)
dev.off()
```

## [Cirrhosis Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by Cirrhosis]{style="color:#51366a; font-weight:bold;"}

```{r OS_Cirrhosis, echo=TRUE, cache=TRUE}
# OS Analysis by Cirrhosis
Cirrhosis_OS <- survfit(Surv(OS_Time, OS_Status) ~ Cirrhosis, data = Survival_R)
median_os <- surv_median(Cirrhosis_OS)

Cirrhosis_OS_plot <- create_survival_plot_binary(Cirrhosis_OS, "Cirrhosis", "Cirrhosis", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "No", "Yes")

# Display plot
print(Cirrhosis_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Cirrhosis_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Cirrhosis_OS_plot)
dev.off()
```

### [Progression-Free Survival by Cirrhosis]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Cirrhosis, echo=TRUE, cache=TRUE}
# PFS Analysis by Cirrhosis
Cirrhosis_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Cirrhosis, data = Survival_R)
median_pfs <- surv_median(Cirrhosis_PFS)

Cirrhosis_PFS_plot <- create_survival_plot_binary(Cirrhosis_PFS, "Cirrhosis", "Cirrhosis", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "No", "Yes")

# Display plot
print(Cirrhosis_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Cirrhosis_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Cirrhosis_PFS_plot)
dev.off()
```

## [Viral vs. Non Viral Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by Viral vs. Non Viral]{style="color:#51366a; font-weight:bold;"}

```{r OS_Viral, echo=TRUE, cache=TRUE}
# OS Analysis by Viral vs. Non-Viral
Viral_OS <- survfit(Surv(OS_Time, OS_Status) ~ Viral, data = Survival_R)
median_os <- surv_median(Viral_OS)

Viral_OS_plot <- create_survival_plot_binary(Viral_OS, "Viral", "Viral", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "Non-Viral", "Viral")

# Display plot
print(Viral_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Viral_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Viral_OS_plot)
dev.off()
```

### [Progression-Free Survival by Viral vs. Non Viral]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Viral, echo=TRUE, cache=TRUE}
# PFS Analysis by Viral vs. Non Viral
Viral_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Viral, data = Survival_R)
median_pfs <- surv_median(Viral_PFS)

Viral_PFS_plot <- create_survival_plot_binary(Viral_PFS, "Viral Status", "Viral", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "Non-Viral", "Viral")

# Display plot
print(Viral_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Viral_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Viral_PFS_plot)
dev.off()
```

## [Aetiology Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by Aetiology]{style="color:#51366a; font-weight:bold;"}

```{r OS_Aetiology, echo=TRUE, cache=TRUE}
# OS Analysis by Aetiology
#Aetiology_OS <- survfit(Surv(OS_Time, OS_Status) ~ Aetiology, data = Survival_R)
#median_os <- surv_median(Aetiology_OS)

#Aetiology_OS_plot <- create_survival_plot(Aetiology_OS, "Aetiology", "Aetiology", median_os, "OS_Time", "OS_Status", 
#                                   "OS Probability", 80, 0.95, 0.75, 0.55, 0.35)

# Display plot
#print(Aetiology_OS_plot)

# Save plot
#png("Aetiology_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
#print(Aetiology_OS_plot)
#dev.off()
```

### [Progression-Free Survival by Aetiology]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Aetiology, echo=TRUE, cache=TRUE}
# PFS Analysis by Aetiology
#Aetiology_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Aetiology, data = Survival_R)
#median_pfs <- surv_median(Aetiology_PFS)

#Aetiology_PFS_plot <- create_survival_plot(Aetiology_PFS, "Aetiology", "Aetiology", median_pfs, "PFS_Time", "PFS_Status", 
#                                    "PFS Probability", 40, 0.97, 0.77, 0.57, 0.40)

# Display plot
#print(Aetiology_PFS_plot)

# Save plot
#png("Aetiology_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
#print(Aetiology_PFS_plot)
#dev.off()
```

## [Tumour size Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by Tumour size]{style="color:#51366a; font-weight:bold;"}

```{r OS_Tumour, echo=TRUE, cache=TRUE}
# OS Analysis by Tumor Size
Tumour_OS <- survfit(Surv(OS_Time, OS_Status) ~ Tumour_size, data = Survival_R)
median_os <- surv_median(Tumour_OS)

Tumour_OS_plot <- create_survival_plot_binary(Tumour_OS, "Tumour Size", "Tumour_size", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "<5 cm", "≥5 cm")

# Display plot
print(Tumour_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Tumour_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Tumour_OS_plot)
dev.off()
```

### [Progression-Free Survival by Tumour size]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Tumour, echo=TRUE, cache=TRUE}
# PFS Analysis by Tumor Size
Tumour_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Tumour_size, data = Survival_R)
median_pfs <- surv_median(Tumour_PFS)

Tumour_PFS_plot <- create_survival_plot_binary(Tumour_PFS, "Tumor Size", "Tumour_size", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "<5 cm", "≥5 cm")

# Display plot
print(Tumour_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Tumour_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Tumour_PFS_plot)
dev.off()
```

## [AFP Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by AFP]{style="color:#51366a; font-weight:bold;"}

```{r OS_AFP, echo=TRUE, cache=TRUE}
# OS Analysis by AFP
AFP_OS <- survfit(Surv(OS_Time, OS_Status) ~ AFP_binary, data = Survival_R)
median_os <- surv_median(AFP_OS)

AFP_OS_plot <- create_survival_plot_binary(AFP_OS, "AFP", "AFP_binary", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "<400 ng/mL", "≥400 ng/mL")

# Display plot
print(AFP_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/AFP_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(AFP_OS_plot)
dev.off()
```

### [Progression-Free Survival by AFP]{style="color:#51366a; font-weight:bold;"}

```{r PFS_AFP, echo=TRUE, cache=TRUE}
# PFS Analysis by AFP
AFP_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ AFP_binary, data = Survival_R)
median_pfs <- surv_median(AFP_PFS)

AFP_PFS_plot <- create_survival_plot_binary(AFP_PFS, "AFP", "AFP_binary", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "<400 ng/mL", "≥400 ng/mL")

# Display plot
print(AFP_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/AFP_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(AFP_PFS_plot)
dev.off()
```

## [Albumin Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by Albumin]{style="color:#51366a; font-weight:bold;"}

```{r OS_Albumin, echo=TRUE, cache=TRUE}
# OS Analysis by Albumin
Albumin_OS <- survfit(Surv(OS_Time, OS_Status) ~ Albumin_binary, data = Survival_R)
median_os <- surv_median(Albumin_OS)

Albumin_OS_plot <- create_survival_plot_binary(Albumin_OS, "Albumin", "Albumin_binary", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "<36 g/L", "≥36 g/L")

# Display plot
print(Albumin_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Albumin_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Albumin_OS_plot)
dev.off()
```

### [Progression-Free Survival by Albumin]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Albumin, echo=TRUE, cache=TRUE}
# PFS Analysis by Albumin
Albumin_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Albumin_binary, data = Survival_R)
median_pfs <- surv_median(Albumin_PFS)

Albumin_PFS_plot <- create_survival_plot_binary(Albumin_PFS, "Albumin", "Albumin_binary", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "<36 g/L", "≥36 g/L")

# Display plot
print(Albumin_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Albumin_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Albumin_PFS_plot)
dev.off()
```

## [Bilirubin Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by Bilirubin]{style="color:#51366a; font-weight:bold;"}

```{r OS_Bilirubin, echo=TRUE, cache=TRUE}
# OS Analysis by Bilirubin
Bilirubin_OS <- survfit(Surv(OS_Time, OS_Status) ~ Bilirubin_binary, data = Survival_R)
median_os <- surv_median(Bilirubin_OS)

Bilirubin_OS_plot <- create_survival_plot_binary(Bilirubin_OS, "Bilirubin", "Bilirubin_binary", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "<11 μmol/L", "≥11 μmol/L")

# Display plot
print(Bilirubin_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Bilirubin_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Bilirubin_OS_plot)
dev.off()
```

### [Progression-Free Survival by Bilirubin]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Bilirubin, echo=TRUE, cache=TRUE}
# PFS Analysis by Bilirubin
Bilirubin_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Bilirubin_binary, data = Survival_R)
median_pfs <- surv_median(Bilirubin_PFS)

Bilirubin_PFS_plot <- create_survival_plot_binary(Bilirubin_PFS, "Bilirubin", "Bilirubin_binary", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "<11 μmol/L", "≥11 μmol/L")

# Display plot
print(Bilirubin_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Bilirubin_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Bilirubin_PFS_plot)
dev.off()
```

## [TACE response Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by TACE response]{style="color:#51366a; font-weight:bold;"}

```{r OS_TACE_Response, echo=TRUE, cache=TRUE}
# OS Analysis by Treatment Response
Response_OS <- survfit(Surv(OS_Time, OS_Status) ~ Response, data = Survival_R)
median_os <- surv_median(Response_OS)

Response_OS_plot <- create_survival_plot_binary(Response_OS, "Treatment Response", "Response", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "No Response", "Response")

# Display plot
print(Response_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Response_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Response_OS_plot)
dev.off()
```

### [Progression-Free Survival by TACE response]{style="color:#51366a; font-weight:bold;"}

```{r PFS_TACE_Response, echo=TRUE, cache=TRUE}
# PFS Analysis by Treatment Response
Response_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Response, data = Survival_R)
median_pfs <- surv_median(Response_PFS)

Response_PFS_plot <- create_survival_plot_binary(Response_PFS, "Treatment Response", "Response", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "No Response", "Response")

# Display plot
print(Response_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Response_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Response_PFS_plot)
dev.off()
```

## [Age Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by Age]{style="color:#51366a; font-weight:bold;"}

```{r OS_Age, echo=TRUE, cache=TRUE}
# OS Analysis by Age
Age_OS <- survfit(Surv(OS_Time, OS_Status) ~ Age_binary, data = Survival_R)
median_os <- surv_median(Age_OS)

Age_OS_plot <- create_survival_plot_binary(Age_OS, "Age", "Age_binary", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "<69 years", "≥69 years")

# Display plot
print(Age_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Age_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Age_OS_plot)
dev.off()
```

### [Progression-Free Survival by Age]{style="color:#51366a; font-weight:bold;"}

```{r PFS_Age, echo=TRUE, cache=TRUE}
# PFS Analysis by Age
Age_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ Age_binary, data = Survival_R)
median_pfs <- surv_median(Age_PFS)

Age_PFS_plot <- create_survival_plot_binary(Age_PFS, "Age", "Age_binary", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "<69 years", "≥69 years")

# Display plot
print(Age_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/Age_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(Age_PFS_plot)
dev.off()
```

## [PVT Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by PVT]{style="color:#51366a; font-weight:bold;"}

```{r OS_PVT, echo=TRUE, cache=TRUE}
# OS Analysis by PVT
PVT_OS <- survfit(Surv(OS_Time, OS_Status) ~ PVT, data = Survival_R)
median_os <- surv_median(PVT_OS)

PVT_OS_plot <- create_survival_plot_binary(PVT_OS, "PVT", "PVT", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "No", "Yes")

# Display plot
print(PVT_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/PVT_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(PVT_OS_plot)
dev.off()
```

### [Progression-Free Survival by PVT]{style="color:#51366a; font-weight:bold;"}

```{r PFS_PVT, echo=TRUE, cache=TRUE}
# PFS Analysis by PVT
PVT_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ PVT, data = Survival_R)
median_pfs <- surv_median(PVT_PFS)

PVT_PFS_plot <- create_survival_plot_binary(PVT_PFS, "Portal Vein Thrombosis", "PVT", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "No", "Yes")

# Display plot
print(PVT_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/PVT_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(PVT_PFS_plot)
dev.off()
```

## [cfDNA level Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Overall Survival by cfDNA level]{style="color:#51366a; font-weight:bold;"}

```{r OS_cfDNA, echo=TRUE, cache=TRUE}
# OS Analysis by cfDNA level
cfDNA_OS <- survfit(Surv(OS_Time, OS_Status) ~ cfDNA, data = Survival_R)
median_os <- surv_median(cfDNA_OS)

cfDNA_OS_plot <- create_survival_plot_binary(cfDNA_OS, "cfDNA Level", "cfDNA", median_os, "OS_Time", "OS_Status", 
                                  "OS Probability", 80, 0.95, 0.75, 0.55, "<544 ng/mL", "≥544 ng/mL")

# Display plot
print(cfDNA_OS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/cfDNA_OS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(cfDNA_OS_plot)
dev.off()
```

### [Progression-Free Survival by cfDNA level]{style="color:#51366a; font-weight:bold;"}

```{r PFS_cfDNA, echo=TRUE, cache=TRUE}
# PFS Analysis by cfDNA level
cfDNA_PFS <- survfit(Surv(PFS_Time, PFS_Status) ~ cfDNA, data = Survival_R)
median_pfs <- surv_median(cfDNA_PFS)

cfDNA_PFS_plot <- create_survival_plot_binary(cfDNA_PFS, "cfDNA Level", "cfDNA", median_pfs, "PFS_Time", "PFS_Status", 
                                   "PFS Probability", 40, 0.97, 0.77, 0.57, "<544 ng/mL", "≥544 ng/mL")

# Display plot
print(cfDNA_PFS_plot)

# Save plot
png("/Volumes/Samsung_SSD_8TB/Projects/Thesis_Chapters/Chapter 1 (cfDNA-TACE for HCC)/TACE_Results/cfDNA_PFS_TACE.png", width = 10, height = 8, units = "in", res = 300)
print(cfDNA_PFS_plot)
dev.off()
```

# [) ☣️ Cox Regression Survival Analysis]{style="color:#000000; font-weight:bold;"} {.tabset .tabset-fade .tabset-pills}

## [Univariate Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [AFP Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_AFP, echo=TRUE, cache=TRUE}
# Convert AFP_binary to factor
Survival_R$AFP_binary <- factor(Survival_R$AFP_binary, levels = c(0, 1), labels = c("low", "high"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_AFP <- coxph(Surv(OS_Time, OS_Status) ~ AFP_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of AFP (ng/mL) level > 400 'high' versus ≤ 400 'low' on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_AFP <- coxph(Surv(PFS_Time, PFS_Status) ~ AFP_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of AFP (ng/mL) level > 400 'high' versus ≤ 400 'low' on PFS"))
```

### [Albumin Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_Albumin, echo=TRUE, cache=TRUE}
# Convert Albumin_binary to factor
Survival_R$Albumin_binary <- factor(Survival_R$Albumin_binary, levels = c(0, 1), labels = c("low", "normal"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_Albumin <- coxph(Surv(OS_Time, OS_Status) ~ Albumin_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Albumin (g/L) level < 36 'low' versus ≥ 36 'normal' on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_Albumin <- coxph(Surv(PFS_Time, PFS_Status) ~ Albumin_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Albumin (g/L) level < 36 'low' versus ≥ 36 'normal' on PFS"))
```

### [Bilirubin Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_Bilirubin, echo=TRUE, cache=TRUE}
# Convert Bilirubin_binary to factor
Survival_R$Bilirubin_binary <- factor(Survival_R$Bilirubin_binary, levels = c(0, 1), labels = c("normal", "elevated"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_Bilirubin <- coxph(Surv(OS_Time, OS_Status) ~ Bilirubin_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Bilirubin (μmol/L) level < 11 'normal' versus ≥ 11 'elevated' on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_Bilirubin <- coxph(Surv(PFS_Time, PFS_Status) ~ Bilirubin_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Bilirubin (μmol/L) level < 11 'normal' versus ≥ 11 'elevated' on PFS"))
```

### [Age Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_Age, echo=TRUE, cache=TRUE}
# Convert Age_binary to factor
Survival_R$Age_binary <- factor(Survival_R$Age_binary, levels = c(0, 1), labels = c("younger", "older"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_Age <- coxph(Surv(OS_Time, OS_Status) ~ Age_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Age < 69 'younger' versus ≥ 69 'older' on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_Age <- coxph(Surv(PFS_Time, PFS_Status) ~ Age_binary, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Age < 69 'younger' versus ≥ 69 'older' on PFS"))
```

### [Performance Status Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_PS, echo=TRUE, cache=TRUE}
# Convert PS to factor
Survival_R$PS <- factor(Survival_R$PS, levels = c(0, 1), labels = c("PS0", "PS1"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_PS <- coxph(Surv(OS_Time, OS_Status) ~ PS, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Performance Status: PS0 versus PS1 on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_PS <- coxph(Surv(PFS_Time, PFS_Status) ~ PS, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Performance Status: PS0 versus PS1 on PFS"))
```

### [Cirrhosis Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_Cirrhosis, echo=TRUE, cache=TRUE}
# Convert Cirrhosis to factor
Survival_R$Cirrhosis <- factor(Survival_R$Cirrhosis, levels = c(0, 1), labels = c("No", "Yes"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_Cirrhosis <- coxph(Surv(OS_Time, OS_Status) ~ Cirrhosis, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Cirrhosis: No versus Yes on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_Cirrhosis <- coxph(Surv(PFS_Time, PFS_Status) ~ Cirrhosis, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Cirrhosis: No versus Yes on PFS"))
```

### [Portal Vein Thrombosis Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_PVT, echo=TRUE, cache=TRUE}
# Convert PVT to factor
Survival_R$PVT <- factor(Survival_R$PVT, levels = c(0, 1), labels = c("No", "Yes"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_PVT <- coxph(Surv(OS_Time, OS_Status) ~ PVT, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Portal Vein Thrombosis: No versus Yes on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_PVT <- coxph(Surv(PFS_Time, PFS_Status) ~ PVT, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Portal Vein Thrombosis: No versus Yes on PFS"))
```

### [Tumor Size Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_Tumour, echo=TRUE, cache=TRUE}
# Convert Tumour_size to factor
Survival_R$Tumour_size <- factor(Survival_R$Tumour_size, levels = c(0, 1), labels = c("small", "large"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_Tumour <- coxph(Surv(OS_Time, OS_Status) ~ Tumour_size, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Tumor Size: < 5 cm 'small' versus ≥ 5 cm 'large' on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_Tumour <- coxph(Surv(PFS_Time, PFS_Status) ~ Tumour_size, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Tumor Size: < 5 cm 'small' versus ≥ 5 cm 'large' on PFS"))
```

### [Viral Status Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_Viral, echo=TRUE, cache=TRUE}
# Convert Viral to factor
Survival_R$Viral <- factor(Survival_R$Viral, levels = c(0, 1), labels = c("Non-Viral", "Viral"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_Viral <- coxph(Surv(OS_Time, OS_Status) ~ Viral, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Viral Status: Non-Viral versus Viral on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_Viral <- coxph(Surv(PFS_Time, PFS_Status) ~ Viral, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Viral Status: Non-Viral versus Viral on PFS"))
```

### [Treatment Response Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_Response, echo=TRUE, cache=TRUE}
# Convert Response to factor (not Response_Code)
Survival_R$Response <- factor(Survival_R$Response, levels = c(0, 1), labels = c("No Response", "Response"))

# Fit the Cox proportional hazards model for Overall Survival (OS) using Response
cox_model_OS_Response <- coxph(Surv(OS_Time, OS_Status) ~ Response, data = Survival_R)
summary(cox_model_OS_Response)

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS) using Response
cox_model_PFS_Response <- coxph(Surv(PFS_Time, PFS_Status) ~ Response, data = Survival_R)
summary(cox_model_PFS_Response)
```

### [CTP Class Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_CTP, echo=TRUE, cache=TRUE}
# Convert CTP to factor
Survival_R$CTP <- factor(Survival_R$CTP, levels = c("A", "B"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_CTP <- coxph(Surv(OS_Time, OS_Status) ~ CTP, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Child-Turcotte-Pugh Class: A versus B on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_CTP <- coxph(Surv(PFS_Time, PFS_Status) ~ CTP, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Child-Turcotte-Pugh Class: A versus B on PFS"))
```

### [BCLC Stage Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_BCLC, echo=TRUE, cache=TRUE}
# Convert BCLC to factor
Survival_R$BCLC <- factor(Survival_R$BCLC, levels = c("A", "B", "C"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_BCLC <- coxph(Surv(OS_Time, OS_Status) ~ BCLC, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Barcelona Clinic Liver Cancer Stage on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_BCLC <- coxph(Surv(PFS_Time, PFS_Status) ~ BCLC, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Barcelona Clinic Liver Cancer Stage on PFS"))
```

### [HAP Score Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_HAP, echo=TRUE, cache=TRUE}
# Convert HAP to factor
Survival_R$HAP <- factor(Survival_R$HAP, levels = c("A", "B", "C", "D"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_HAP <- coxph(Surv(OS_Time, OS_Status) ~ HAP, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Hepatoma Arterial-embolization Prognostic Score on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_HAP <- coxph(Surv(PFS_Time, PFS_Status) ~ HAP, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of Hepatoma Arterial-embolization Prognostic Score on PFS"))
```

### [cfDNA Level Analysis]{style="color:#51366a; font-weight:bold;"}

```{r OS_PFS_Cox_cfDNA, echo=TRUE, cache=TRUE}
# Convert cfDNA to factor
Survival_R$cfDNA <- factor(Survival_R$cfDNA, levels = c(0, 1), labels = c("low", "high"))

# Fit the Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_cfDNA <- coxph(Surv(OS_Time, OS_Status) ~ cfDNA, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of cfDNA Level: < 544 ng/mL 'low' versus ≥ 544 ng/mL 'high' on OS"))

# Fit the Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_cfDNA <- coxph(Surv(PFS_Time, PFS_Status) ~ cfDNA, data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Effect of cfDNA Level: < 544 ng/mL 'low' versus ≥ 544 ng/mL 'high' on PFS"))
```

## [Multivariate Analysis]{style="color:#765543; font-weight:bold;"} {.tabset}

### [Multivariate Analysis for Overall Survival]{style="color:#51366a; font-weight:bold;"}

```{r OS_Cox_Multivariate, echo=TRUE, cache=TRUE}
# Fit multivariate Cox proportional hazards model for Overall Survival (OS)
(cox_model_OS_multi <- coxph(Surv(OS_Time, OS_Status) ~ AFP_binary + Albumin_binary + Bilirubin_binary + 
                             Age_binary + PS + Cirrhosis + PVT + Tumour_size + Viral + 
                             Response_Code + CTP + BCLC + HAP + cfDNA, 
                          data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Multivariate Cox Regression for Overall Survival"))
```

### <span style="color:#51366a; font-weight:bold;"> Multivariate Analysis for Progression-Free Survival

```{r PFS_Cox_Multivariate, echo=TRUE, cache=TRUE}
# Fit multivariate Cox proportional hazards model for Progression-Free Survival (PFS)
(cox_model_PFS_multi <- coxph(Surv(PFS_Time, PFS_Status) ~ AFP_binary + Albumin_binary + Bilirubin_binary + 
                              Age_binary + PS + Cirrhosis + PVT + Tumour_size + Viral + 
                              Response_Code + CTP + BCLC + HAP + cfDNA, 
                           data = Survival_R) %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Multivariate Cox Regression for Progression-Free Survival"))
```

### [Stepwise Model Selection]{style="color:#51366a; font-weight:bold;"}

```{r Stepwise_Model, echo=TRUE, cache=TRUE}
# Stepwise model selection for OS
full_model_OS <- coxph(Surv(OS_Time, OS_Status) ~ AFP_binary + Albumin_binary + Bilirubin_binary + 
                        Age_binary + PS + Cirrhosis + PVT + Tumour_size + Viral + 
                        Response_Code + CTP + BCLC + HAP + cfDNA, 
                     data = Survival_R)

step_model_OS <- step(full_model_OS, direction = "both", trace = 0)
(step_model_OS %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Stepwise Selected Model for Overall Survival"))

# Stepwise model selection for PFS
full_model_PFS <- coxph(Surv(PFS_Time, PFS_Status) ~ AFP_binary + Albumin_binary + Bilirubin_binary + 
                         Age_binary + PS + Cirrhosis + PVT + Tumour_size + Viral + 
                         Response_Code + CTP + BCLC + HAP + cfDNA, 
                      data = Survival_R)

step_model_PFS <- step(full_model_PFS, direction = "both", trace = 0)
(step_model_PFS %>%
  tbl_regression(exp = TRUE) %>%
  modify_header(label = "Stepwise Selected Model for Progression-Free Survival"))
```


# [) 🫣 Summary and Conclusions]{style="color:#000000; font-weight:bold;"} {.tabset}

[4.1 Key Findings]{style="color:#3A75C4; font-weight:bold;"}

::::: {.section-box .primary-box}
::: {style="font-weight:bold; color:#1A4F8B; margin-bottom:5px;"}
Summary of Results
:::

<div>

This section will summarize the key findings from the survival analysis of HCC patients treated with TACE.

</div>
:::::

[4.2 Clinical Implications]{style="color:#3A75C4; font-weight:bold;"}

::::: {.section-box .secondary-box}
::: {style="font-weight:bold; color:#2E7D32; margin-bottom:5px;"}
Impact on Practice
:::

<div>

Discuss the clinical implications of these results for HCC treatment with TACE.

</div>
:::::
# <span style="color:#000000; font-weight:bold;">⛴️ Indexes</span> {.unnumbered}


```{=html}
<style>
/* --- :root contains all our variables for easy management --- */
:root {
  /* Default Box Colors */
  --box-bg-color: #f8f9fa;
  --box-border-color: #dee2e6;
  --box-text-color: #212529; /* Darker text for better contrast */
  
  /* Primary Theme */
  --primary-bg: #eef2ff; /* Slightly darker for contrast */
  --primary-border: #6a82fb;

  /* Secondary Theme */
  --secondary-bg: #e6f8ee;
  --secondary-border: #4caf50;
  
  /* Info Theme */
  --info-bg: #e4f4ff;
  --info-border: #2196F3;
  
  /* Warning Theme */
  --warning-bg: #fff8e1;
  --warning-border: #ffc107;
}

/* --- General Box Styling (now uses variables) --- */
.section-box {
  background-color: var(--box-bg-color);
  border-left-color: var(--box-border-color);
  color: var(--box-text-color);
  
  padding: 1.25em;
  margin-bottom: 20px;
  border-radius: 8px;
  border-left-width: 5px;
  border-left-style: solid;
  box-shadow: 0 4px 6px rgba(0, 0, 0, 0.08);
  transition: all 0.3s ease-in-out;
  font-family: -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif;
  overflow: hidden;
}

.section-box:hover {
  transform: translateY(-3px);
  box-shadow: 0 6px 12px rgba(0, 0, 0, 0.12);
}

/* --- Specific Box Themes (now just set variables) --- */
.primary-box {
  --box-bg-color: var(--primary-bg);
  --box-border-color: var(--primary-border);
}

.secondary-box {
  --box-bg-color: var(--secondary-bg);
  --box-border-color: var(--secondary-border);
}

.info-box {
  --box-bg-color: var(--info-bg);
  --box-border-color: var(--info-border);
}

.warning-box {
  --box-bg-color: var(--warning-bg);
  --box-border-color: var(--warning-border);
}
</style>
```